Basics of Hardware Cache Optimization

### 2017-05-31 tex/types.tex
Put datavisualization configuration into new file

% XXX: hacks!  Explicit placement specifier without `t` (top) to prevent the figure from
% interrupting the source code listing.
\begin{figure}%[hbp]
   \centering
   \begin{tikzpicture}
      \datavisualization[%
         scientific axes=clean,
         x axis={%
            logarithmic,
            ticks={major={
               /pgf/number format/int detect,
               at={
                  2048 as 2, 8192 as 8, 32768 as \textbf{32}, 131072 as 128,
                  524288 as \textbf{512}, 2097152 as \pgfmathprintnumber{2048},
                  8388608 as \pgfmathprintnumber{8192},
                  33554432 as \pgfmathprintnumber{32768},
                  134217728 as \pgfmathprintnumber{131072},
                  % $128\cdot 2^{10}$}}},
                  % $2^{17}$}}},
            }}},
            grid={at={32768, 524288}},
            label={Array Size (KiB)},
            length=0.8\textwidth},
         y axis={include value=0, label={Cycles / Iteration}, length=6cm, grid=at ticks},
         visualize as scatter,
         scatter={style={mark=*, mark options={scale=.65}}}]
         data [read from file=access-times/access-times.csv, separator=\space];
   \end{tikzpicture}
   % \caption{Access Times for Random Reads (\Cref{lst:access-times})}
   \caption{Access Times for Random Reads}
   \label{fig:access-times}
\end{figure}

>>>>

\begin{figure}
   \centering
   \tikz \datavisualization[array size vs cycles plot]
      data [read from file=access-times/access-times.csv, separator=\space];
   % \caption{Access Times for Random Reads (\Cref{lst:access-times})}
   \caption{Access Times for Random Reads}
   \label{fig:access-times}
\end{figure}
